\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}  %for picture insert add by msc
\usepackage{float}
\usepackage{booktabs}  %for table line , add by msc
\usepackage{textcomp}
\newtheorem{theorem}{\textbf{Theorem}}
\newtheorem{definition}{\textbf{Definition}}
\newtheorem{lemma}{\textbf{Lemma}}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm
\begin{document}
\title{Optimization Approach Allocation for Network Slicing in 5G \\}

\begin{abstract}
这篇论文的重点要放在network slicing上，重点不能是NFV 和SDN，这只是背景，交代说是这些技术支撑了网络切片，但是我的主要工作，应该是资源分配，因为这才是我们能做的事情，文章主要以5G network slicing为背景，考虑网络，存储，计算，电力等几种资源，来建立一个优化模型，利用深度强化学习的方法，对优化问题进行求解，从而提供为网络切片一个高效的策略。
主要的贡献有：1，建立了一个网络切片的模型；2，考虑了多种情况，可以引入节日状态；3，利用深度强化学习的方法进行求解。

\end{abstract}
\section{Introduction}

第一段：介绍5G的三大应用场景，为了引出需求多样化
5G网络要解决的问题，不单单是网速提高的问题。他要面临多个场景应用的挑战。目前根据3GPP的规定，主要有三大应用场景，不同的场景的性能要求，分别是什么。
那么5G要想满足这些应用的性能的需求，就需要多样化的资源分配方案，不能向4G那样的
We need to allocated three types of resources. they are network, compute and storage.
I need to read sdran network . and do some model building work.

第二段：针对需求多样化的问题，怎样才能满足性能需求，提出网络切片技术
这里可以是相关工作，我可以不要相关工作这一节。
We assume total bandwidth in the network is $B$Hz.
According to Shannon capacity formula,

第三段：现有的网络切片都做成什么样？还有那些不足，我的motivation在哪！
In article [], the virtual RAN was proposed to abstract the network resources.

第四段：本文都干了那些工作，用了什么方法什么理论，得到了什么结果，结果的意义是什么？main contribution。

第五段：文档结构说明


\section{System Model}


\section{Network Slicing}
A 5G network slicing management might organize the resource and allocated them for various application requests.
We assume that the system has a constant amount of resources. The network slicing request resources from system according to application requires, and every network slicing has its tenancy period.

Based on this assumption, we seem system resources as a box with the cuboid shape. The height of the box $H$ represents the computing capacity in the whole system. The width of the box $W$ represents the bandwidth provided by the network. The length of the box $L$ is the time axis, and it can accommodate the tenancy period of network slicing. The network slices are seemed as small boxes filled in the system cuboid. Network slicing is like putting as many different sizes small boxes as possible into the big cuboid of the system.
%现在开始写network slicing的表达；

We define a network slicing request as $S_{i} = \{C, B, T, i\}$, where $C$ is the requirements of the computing resource, $B$ is the amount of bandwidth required by network slice, $T$ is the tenancy period of this network slice, it is the time of the resource occupation, $i$ is used to identify the application who request the network slice.

Many diverse applications in the system for network slicing management to select and serve. In our model, we choose some of the applications as $I$ to be allocated the network slice. Each application has its own attribute, and the definition is as $i\in I, I_{i} = \{F, t\}$, where $F$ is the data size of the application need to be computed and transferred, $t$ is the maximum delay required by the application. When an application $i$ has been finished within the delay successfully, it can provide a profit $p_{i}$. Our objective is to maximize the system resource utility in a certain time period. Next, we derive our model.

%, the delay contains computing time and transmission time
Firstly, the resources in the network slice allocated to application need to satisfy the performance requirement. The delay of application $t_{i}$ includes two parts, the computing time cost and the transmission time cost. The computing time cost depends on the data size $F_{i}$ and the computing rate $C_{i}$, the ratio $\frac{F_{i}}{C_{i}}$ is the computing time. The transmission time cost relies on data size $F_{i}$ and the transmission rate which lie on the allocated bandwidth $B_{i}$. The sum of two time costs must less than or equal to threshold of delay $t_{i}$.
Secondly, the number of system resources is constant for a built network. Therefore, the computing capacity and bandwidth of network slice are both limited by system resources. The system resource utilization are considered in a certain period, so the whole duration of network slices need to be within the certain period.%special time.
Finally, the $S_{i}$ corresponds to the cubage of allocated network slice $i$. The slices should not overlap with each other, in order to guarantee the applications occupy their own resources. 
Then we can formulate our network slicing problem as follows

\begin{align}
maximize\quad &\sum_{i=1}^{I} p_{i}\cdot S_{i} \\
subject\quad to\quad&\sum_{i=1}^{I} C_{i} \leq H; \\
&\sum_{i=1}^{I} B_{i} \leq W; \\
&\sum_{i=1}^{I} T_{i} \leq L; \\
&\frac{F_{i}}{C_{i}}+\frac{F_{i}}{B_{i}} \leq t_{i}; \\
&R_{i} \cap R_{j} = {\O},  i,j \in I, \forall i\neq j;
\end{align}


%the resource contains three types: network, computing, and storage. 因为我的这个模型中，没有存储的概念

\end{document}
